Objectification Special Studies Analysis

### 2019-03-26 full analysis file.Rmd
testing

```{r}
model <- '#####regressions 
howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P
howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A
authenticity_A ~ d*howbody_avg_A
authenticity_P ~ d*howbody_avg_P
trigram_score_A ~ e1*authenticity_A
careerasp_A ~ e2*authenticity_A
relag_A ~ e3*authenticity_A
trigram_score_P ~ e1*authenticity_P
careerasp_P ~ e2*authenticity_P
relag_P ~ e3*authenticity_P
######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
trigram_score_A ~~ trigram_score_P
careerasp_A ~~ careerasp_P
relag_A ~~ relag_P
trigram_score_A ~~ 0*careerasp_A
trigram_score_A ~~ 0*relag_A
trigram_score_A ~~ 0*careerasp_P
trigram_score_A ~~ 0*relag_P
careerasp_A ~~ 0*relag_A
careerasp_A ~~ 0*trigram_score_P
careerasp_A ~~ 0*relag_P
relag_A ~~ 0*trigram_score_P
relag_A ~~ 0*careerasp_P
trigram_score_P ~~ 0*careerasp_P
trigram_score_P ~~ 0*relag_P
careerasp_P ~~ 0*relag_P
#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
'
#hi
fit <- sem(model, data=dyad_cswomen)
summary(fit)
```

>>>>

```{r}
model <- '#####regressions 
howbody_avg_A ~ t*TSO_A + a*a2pSOO_A + b*a2pSOO_P
howbody_avg_P ~ t*TSO_P + a*a2pSOO_P + b*a2pSOO_A
authenticity_A ~ d*howbody_avg_A
authenticity_P ~ d*howbody_avg_P
trigram_score_A ~ e1*authenticity_A
careerasp_A ~ e2*authenticity_A
relag_A ~ e3*authenticity_A
trigram_score_P ~ e1*authenticity_P
careerasp_P ~ e2*authenticity_P
relag_P ~ e3*authenticity_P
######covariances
#endogenous
howbody_avg_A ~~ howbody_avg_P
authenticity_A ~~ authenticity_P
trigram_score_A ~~ trigram_score_P
careerasp_A ~~ careerasp_P
relag_A ~~ relag_P
trigram_score_A ~~ 0*careerasp_A
trigram_score_A ~~ 0*relag_A
trigram_score_A ~~ 0*careerasp_P
trigram_score_A ~~ 0*relag_P
careerasp_A ~~ 0*relag_A
careerasp_A ~~ 0*trigram_score_P
careerasp_A ~~ 0*relag_P
relag_A ~~ 0*trigram_score_P
relag_A ~~ 0*careerasp_P
trigram_score_P ~~ 0*careerasp_P
trigram_score_P ~~ 0*relag_P
careerasp_P ~~ 0*relag_P
#####variances
howbody_avg_A ~~ v1*howbody_avg_A
howbody_avg_P ~~ v1*howbody_avg_P
TSO_A ~~ v2*TSO_A
TSO_P ~~ v2*TSO_P
a2pSOO_A ~~ v3*a2pSOO_A
a2pSOO_P ~~ v3*a2pSOO_P
authenticity_A ~~ v4*authenticity_A
authenticity_P ~~ v4*authenticity_P
##endogenous intercepts
howbody_avg_A ~ i*1
howbody_avg_P ~ i*1
authenticity_A ~ i2*1
authenticity_P ~ i2*1
trigram_score_A ~ i3*1
trigram_score_P ~ i4*1
careerasp_A ~ i5*1
careerasp_P ~ i5*1
relag_A ~ i6*1
relag_P ~ i6*1
##exogenous means
TSO_A ~ m*1
TSO_P ~ m*1
a2pSOO_A ~ m2*1
a2pSOO_P ~ m2*1
TSO_P_SOO_A ~ m3*1
TSO_A_SOO_P ~ m3*1
## exogenous covariances
TSO_A_SOO_P ~~ c1*TSO_A
TSO_P_SOO_A ~~ c1*TSO_P
TSO_A_SOO_P ~~ c2*a2pSOO_P
TSO_P_SOO_A ~~ c2*a2pSOO_A
TSO_A ~~ c3*a2pSOO_P
TSO_P ~~ c3*a2pSOO_A
TSO_A ~~ c4*a2pSOO_A
TSO_P ~~ c4*a2pSOO_P
'

fit <- sem(model, data=dyad_cswomen)
summary(fit)
```
